---
title: "Replication code for: Assessment Of A Cost-Effective Headphone Calibration Procedure For Soundscape Evaluations"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)

library(dplyr)
library(plyr)
library(readr)
library(ggplot2)
library(reshape2)
library(tidyr)                      
                      
```

## Data Preparation

The survey data was collected via a matlab GUI (https://github.com/kenowr/satp-gui). The data from each participant is stored in a single csv file. All participants' data would be merged into a single dataframe.

```{r dataloader}

#merge all csv files
allcsvnames <- list.files(path = "./UCL Result",
                        pattern = "*.csv", full.names = TRUE)
satpMalay <- ldply(allcsvnames,read.csv,header=FALSE)

#extract participant ID
participantID <- as.numeric(gsub(".*?([0-9]+).*", 
                                 "\\1", allcsvnames))
noOfStimuli <- 27
participantIDvec <- rep(1:length(participantID), each=noOfStimuli)

satpMalay<-cbind(participantIDvec,satpMalay)

colnames(satpMalay)<-c("participantID","stimuliID",
                      "pleasant", "chaotic",
                      "vibrant","uneventful",
                      "calm", "annoying",
                      "eventful","monotonous",
                      "check","duration")

satpMalayClean<- satpMalay %>%
        filter(participantID!=4) %>%
        filter(participantID!=16)

#export csv
write.csv(x=satpMalayClean,
          file = "SATPMalayP2_NTU.csv",
          row.names = FALSE)

```

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
